QPLIB: A Library of Quadratic Programming Instances

### 2018-02-04 QPLIB-1.0.tex
Update QPLIB-1.0.tex
fix typos

However, this diversity also implies that QP means very different things to different researchers. This is illustrated by the fact that the class of problems that we simply refer to here as ``QP'' might more accurately be called Mixed-Integer Quadratically-Constrained Quadratic Programming (MIQCQP) in the most general case. It is, therefore, perhaps not surprising that, unlike for ``simpler'' problems classes \cite{Koch2011},  there has been, to date, no single library devoted to all different kinds of instances of QP. While several specialised libraries devoted to particular cases of QP are available, each of them is either focussed on a particular application (a specific problem that can be modelled as a QP), or on QPs with specific structural properties that make them suitable for solution by some given class of algorithmic approaches. To the best of our knowledge, collecting a set of QP instances that is at the same time not overwhelmingly onerous but sufficiently challenging for the many different interested communities has not been attempted. This work constitutes a first step in this direction.

@@

%\multicolumn{3}{l}{Process networks optimisation problems typically involve two} \\

@@

Controlled Tabular Adjustment & \checkmark & \cite{CaFG14}

>>>>

However, this diversity also implies that QP means very different things to different researchers. This is illustrated by the fact that the class of problems that we simply refer to here as ``QP'' might more accurately be called Mixed-Integer Quadratically-Constrained Quadratic Programming (MIQCQP) in the most general case. It is, therefore, perhaps not surprising that, unlike for ``simpler'' problems classes \cite{Koch2011},  there has been, to date, no single library devoted to all different kinds of instances of QP. While several specialized libraries devoted to particular cases of QP are available, each of them is either focused on a particular application (a specific problem that can be modeled as a QP), or on QPs with specific structural properties that make them suitable for solution by some given class of algorithmic approaches. To the best of our knowledge, collecting a set of QP instances that is at the same time not overwhelmingly onerous but sufficiently challenging for the many different interested communities has not been attempted. This work constitutes a first step in this direction.

@@

%\multicolumn{3}{l}{Process networks optimization problems typically involve two} \\

@@

Controlled Tabular Adjustment & \checkmark & \cite{CaFG14} \\
\multicolumn{3}{l}{\textbf{Trust-region methods}} \\[1pt]
Trust-region subproblem & & \cite{hager2001,Gould1999,Rendl1997,Erway2010,Adachi2017,Gould2010}\\
\multicolumn{3}{l}{\textbf{PDE-constrained optimization}} \\[1pt]
Optimal control problem & & \cite{DIPILLO1983101,Stojanovic1991,Schittkowski1979}

### 2018-02-04 conclusion.tex
fix typos

 This manuscript describes the first comprehensive library of instances for Quadratic Programming (QP). Since QP comprises  different and ``varied'' categories of problems, we proposed a classification and we briefly discuss the main classes of solution methods for QP.

We then describe the steps of the adopted process used to filter the gathered instances  in order to build the new library. Our design goals were to build a library which is computationally challenging and as broad as possible, i.e., it represents the largest possible categories of QP problems, while remaining of manageable size. We have also proposed a stand-alone QP format that is intended
for the convenient exchange and use of our QP instances.

We want to stress once again that we intentionally avoid to perform a computational comparison of the performances of the different solvers. Our goal is instead to provide a common test-bed of instances for practitioners and researchers in the field. This new library will hopefully serve as a point of reference to test new ideas and algorithms for QP problems.

>>>>

This manuscript described the first comprehensive library of instances for Quadratic Programming (QP). Since QP comprises  different and ``varied'' categories of problems, we proposed a classification and we briefly discussed the main classes of solution methods for QP.

We then described the steps of the adopted process used to filter the gathered instances  in order to build the new library. Our design goals were to build a library which is computationally challenging and as broad as possible, i.e., it represents the largest possible categories of QP problems, while remaining of manageable size. We have also proposed a stand-alone QP format that is intended
for the convenient exchange and use of our QP instances.

We want to stress once again that we intentionally avoided to perform a computational comparison of the performances of the different solvers. Our goal was instead to provide a common test bed of instances for practitioners and researchers in the field. This new library will hopefully serve as a point of reference to test new ideas and algorithms for QP problems.

### 2018-02-04 methods.tex
fix typos

Complete methods are often referred to as \emph{exact} in a large part of the mathematical optimization community. This term has to be used with care, as it implicitly makes assumptions on the underlying computational model that may not be acceptable in all cases. For example, te decision version of \textit{QCL} is known to be in the complexity class \textbf{NP} \cite{vavasis90a}, whereas the same is not known about \textit{LCQ}, even with zero objective. On the other hand, there exists a method for deciding feasibility of systems of polynomial equations and inequalities \cite{tarski-reals}, including the solution of \textit{LCQ} with zero objective function.

>>>>

Complete methods are often referred to as \emph{exact} in a large part of the mathematical optimization community. This term has to be used with care, as it implicitly makes assumptions on the underlying computational model that may not be acceptable in all cases. For example, the decision version of \textit{QCL} is known to be in the complexity class \textbf{NP} \cite{vavasis90a}, whereas the same is not known about \textit{LCQ}, even with zero objective. On the other hand, there exists a method for deciding feasibility of systems of polynomial equations and inequalities \cite{tarski-reals}, including the solution of \textit{LCQ} with zero objective function.
